Re-run, Repeat, Reproduce, Reuse, Replicate:\\Transforming Code into Scientific Contributions

### 2017-08-24 draft.tex
Update codes from random-walk repository

x = 0
for i in xrange(10):
    step = random.choice([-1,+1])
    x += step
    print x,
\end{code}
\end{minipage}

Executed, this program would display:
\begin{code}{Output}
-1 0 -1 -2 -1 -2 -1 -2 -3 -4 # with the steps being -1, +1, -1, -1, +1, -1, +1, -1, -1,  -1
\end{code}

@@

walk, total = [], 0
for i in range(10):
    step = random.choice([-1,+1])
    total += step
    walk.append(total)

@@

x =  0
path = []
for i in range(10):
    step = random.choice([-1,+1])
    x += step
    path.append(x)

print(path)
# Saving output to disk
with open("results-R2.txt", "w") as fd:
    fd.write(str(path))

\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 4:}} Re-runnable, repeatable, reproducible random walk (R$^3$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C. Y. Benureau
# Release under the BSD 2-clause license
# Tested with CPython 3.6.1 / macOS 10.12.4 / 64 bits architecture
import sys, subprocess, datetime, random

def walk():
    path = []
    x = 0
    for i in range(10):
        if random.uniform(-1,+1) > 0:
            x = x + 1
        else:
            x = x - 1
        path.append(x)
    return path

# If repository is dirty, don't run anything
if subprocess.call(("git", "diff-index", "--quiet", "HEAD")):
    print("Repository is dirty, please commit first")
    sys.exit(1)

# Get git hash if any
revision = subprocess.check_output(("git", "rev-parse", "HEAD"))

# Unit test
random.seed(1)
assert walk() == [-1, 0, 1, 0, -1, -2, -1, 0, -1, -2]

# Random walk for 10 steps
seed = 1
random.seed(seed)
path = walk()

# Display & save results
print(path)
results = { 'data':      path,
            'seed':      seed,
            'timestamp': str(datetime.datetime.utcnow()),
            'revision':  revision,
            'system' :   sys.version }
with open("results-R3.txt", "w") as fd:
    fd.write(str(results))
\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 5:}} Re-runnable, repeatable, reproducible, reusable random walk (R$^4$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C. Y. Benureau
# Release under the BSD 2-clause license
# Tested with CPython 3.6.1 / macOS 10.12.4 / 64 bits architecture
import sys, subprocess, datetime, random

def walk(x0=0, step=1, count=10, seed=0):
    """ Random walk
        x0   : initial position (default 0)
        step : step size (default 1)
        count: number of steps (default 10)
        seed : seed for the initialization of the random generator (default 0)
    """
    path, x = [], x0
    random.seed(seed)
    for i in range(count):
        if random.uniform(-1,+1) > 0:
            x = x + step
        else:
            x = x - step
        path.append(x)
    return path

if __name__ == '__main__':
    # If repository is dirty, don't do anything
    if subprocess.call(("git", "diff-index", "--quiet", "HEAD")):
        print("Repository is dirty, please commit first")
        sys.exit(1)

    # Get git hash if any
    revision = subprocess.check_output(("git", "rev-parse", "HEAD"))

    # Unit test checking reproducibility
    assert walk(0, 1, 10, 1) == [-1, 0, 1, 0, -1, -2, -1, 0, -1, -2]

    # Simulation parameters
    parameters = { 'x0':    0,
                   'step':  1,
                   'count': 10,
                   'seed' : 1 }
    path = walk(**parameters)
    results = {'data':       path,
               'parameters': parameters,
               'timestamp':  str(datetime.datetime.utcnow()),
               'revision':   revision,
               'system':     sys.version}

    # Save & display results
    with open("results-R4.txt", "w") as fd:
        fd.write(str(results))

    print(path)
\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 6:}} Replicated random walk (R$^5$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C.Y. Benureau
# Release under the BSD 2-clause license
# Tested with Python 3.6.1 / Numpy 1.12.0 / macOS 10.12.4 / 64 bits architecture
import random
import numpy as np

@@

if __name__ == '__main__':
    # Unit test
    assert walk(n=10, seed=1) == [-1, 0, 1, 0, -1, -2, -1, 0, -1, -2]

@@

    # Save & display results
    results = {'data': path, 'seed': seed}
    with open("results-R5.txt", "w") as fd:
        fd.write(str(results))
    print(path)

\end{code}
\end{minipage}

>>>>

x = 0
for i in xrange(10):
    if random.uniform(-1, +1) > 0:
        x += 1
    else:
        x -= 1
    print x,
\end{code}
\end{minipage}

Executed, this program would display:
\begin{code}{Output}
-1 0 -1 0 -1 0 -1 0 1 2 # with the steps being -1, +1, -1, +1, -1, +1, -1, +1, +1, +1
\end{code}

@@

x =  0
walk = []
for i in range(10):
    if random.uniform(-1, +1) > 0:
        x += 1
    else:
        x -= 1
    walk.append(x)

@@

x =  0
walk = []
for i in range(10):
    if random.uniform(-1, +1) > 0:
        x += 1
    else:
        x -= 1
    walk.append(x)

print(walk)
# Saving output to disk
with open('results-R2.txt', 'w') as fd:
    fd.write(str(walk))
\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 4:}} Re-runnable, repeatable, reproducible random walk (R$^3$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C. Y. Benureau
# Release under the BSD 2-clause license
# Tested with CPython 3.6.2 / macOS 10.12.6 / 64 bits architecture
import sys, subprocess, datetime, random

def generate_walk():
    walk = []
    x = 0
    for i in range(10):
        if random.uniform(-1, +1) > 0:
            x += 1
        else:
            x -= 1
        walk.append(x)
    return walk

# If repository is dirty, don't run anything
if subprocess.call(('git', 'diff-index', '--quiet', 'HEAD')):
    print('Repository is dirty, please commit first')
    sys.exit(1)

# Get git hash if any
revision = subprocess.check_output(('git', 'rev-parse', 'HEAD'))

# Unit test
random.seed(42)
assert generate_walk() == [1, 0, -1, -2, -1, 0, 1, 0, -1, -2]

# Random walk for 10 steps
seed = 1
random.seed(seed)
walk = generate_walk()

# Display & save results
print(walk)
results = {'data'     : walk,
           'seed'     : seed,
           'timestamp': str(datetime.datetime.utcnow()),
           'revision' : revision,
           'system'   : sys.version}
with open('results-R3.txt', 'w') as fd:
    fd.write(str(results))
\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 5:}} Re-runnable, repeatable, reproducible, reusable random walk (R$^4$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C.Y. Benureau
# Release under the BSD 2-clause license
# Tested with CPython 3.6.2 / macOS 10.12.6 / 64 bits architecture
import sys, subprocess, datetime, random

def generate_walk(count, x0=0, step=1, seed=0):
    """ Random walk
        count: number of steps
        x0   : initial position (default 0)
        step : step size (default 1)
        seed : seed for the initialization of the random generator (default 0)
    """
    random.seed(seed)
    x = x0
    walk = []
    for i in range(count):
        if random.uniform(-1, +1) > 0:
            x += 1
        else:
            x -= 1
        walk.append(x)
    return walk

def generate_results(count, x0=0, step=1, seed=0):
    """Compute a walk and return it alongside its context"""
    # If repository is dirty, don't do anything
    if subprocess.call(('git', 'diff-index', '--quiet', 'HEAD')):
        print('Repository is dirty, please commit first')
        sys.exit(1)

    # Get git hash if any
    revision = subprocess.check_output(('git', 'rev-parse', 'HEAD'))

    # Compute results
    walk = generate_walk(count=count, x0=x0, step=step, seed=seed)
    return {'data'      : walk,
            'parameters': {'x0':x0, 'step':step, 'count':count, 'seed':seed},
            'timestamp' : str(datetime.datetime.utcnow()),
            'revision'  : revision,
            'system'    : sys.version}

if __name__ == '__main__':
    # Unit test checking reproducibility (will fail with Python<=3.2)
    assert generate_walk(10, 0, 1, 42) == [1, 0, -1, -2, -1, 0, 1, 0, -1, -2]

    # Simulation parameters
    count, x0, seed = 10, 0, 1
    results = generate_results(count, x0=x0, seed=seed)

    # Save & display results
    with open('results-R4.txt', 'w') as fd:
        fd.write(str(results))
    print(results['data'])
\end{code}
\end{minipage}\\

@@

\noindent \begin{minipage}[c]{\linewidth}
\begin{code}{\textbf{\textsc{Listing 6:}} Replicated random walk (R$^5$)}
# Copyright (c) 2017 Nicolas P. Rougier and Fabien C.Y. Benureau
# Release under the BSD 2-clause license
# Tested with CPython 3.6.2 / NumPy 1.12.0 / macOS 10.12.6 / 64 bits architecture
import random
import numpy as np

@@

if __name__ == '__main__':
    # Unit test
    assert walk(n=10, seed=42) == [1, 0, -1, -2, -1, 0, 1, 0, -1, -2]

@@

    # Save & display results
    results = {'data': path, 'seed': seed}
    with open("results-R5.txt", "w") as fd:
        fd.write(str(results))
    print(path)
\end{code}
\end{minipage}
